The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
add P4 remotely sensed behv to move persp

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations (Hughey et al. 2018).

>>>>

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations (Hughey et al. 2018). Biologging and wildlife tracking technology 
has advanced to the point where relocations can be programmed to occur as 
frequently as each second (Börger 2016), a practice which has been applied 
to questions of collective movement (e.g Strandburg-Peskin et al. 2015). 
Meanwhile, remote sensing technology, including unmanned aerial vehicles 
and satellites, can be used to track the fine-scalemovements of  
groups over large distances and time scales (Torney et al. 2019). Using 
technology to infer behaviour has therefore become standard operating procedure
for many species in many systems. Our ability to collect and process 
remotely sensed data and infer social processes based on animal movement 
provides an opportunity to use multilayer social network analysis to answer
complex questions about animal socioecology.
